### 2019-11-12 cvpr_submission/samnet.tex
Moved all images into cvpr folder. Added model section.

\begin{figure}[b!]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{figure}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=\textwidth]{../img/architecture/samcell_reasoning}
	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
	\label{fig:samcell}
\end{figure}

@@

\noindent{\textbf{Question-driven Controller.}}
This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
The control state $\vec{c}_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
a two-layer feedforward network with ELU activation used in the hidden layer of $d$ units.
The output $\vec{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
For the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.

@@

\noindent{\textbf{Reasoning Unit.}}
%\paragraph{Reasoning Unit.}
This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as
determining the location of the correct object for reasoning.
To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
First, we take the visual attention vector $\vec{va}_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
and compute a simple aggregate\footnote{%
	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
$vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention
vector is, the higher is the aggregate value.
We perform a similar computation on the read head $\rhead_t$ over memory locations.
We feed these two values along with the temporal class weights $\vec{\tau}_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
in $[0,1]$ modulated for the current reasoning step:
(a) $\imatch_t$, which determines whether there is a valid visual object;
(b) $\mmatch_t$, which determines whether there is a valid memory object. 
(c) $\doreplace_t$, which determines whether the memory should be updated by replacing a previously stored object with a new one; and
(d) $\doadd_t$, which determines whether a new object should be added to memory.
We stress that the network has to learn via training how to correctly implement these behaviors.

>>>>

\begin{figure}[b!]
	\centering
	\includegraphics[width=\textwidth]{img/architecture/samnet_architecture4}
	\caption{General architecture of SAMNet}
	\label{fig:samnet}
\end{figure}

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=\textwidth]{img/architecture/samcell_reasoning}
	\caption{Unfolded reasoning steps with operations performed by the SAMCell}
	\label{fig:samcell}
\end{figure}

@@

\noindent{\textbf{Question-driven Controller.}}
This module drives attention over the question to produce $k$ control states, one per reasoning operation. 
The control state $\vec{c}_t$ at step $t$ is then fed to a \emph{temporal classifier}, 
a two-layer feedforward network with ELU activation used in the hidden layer of $d$ units.
The output $\bm{\tau}_t$ of the classifier is intended to represent the different temporal contexts (or lack thereof) associated with the word in focus for that step of reasoning.	
For the COG dataset we pick 4 classes to capture the terms labeled ``last'', ``latest'', ``now'', and ``none''.

@@

\noindent{\textbf{Reasoning Unit.}}
%\paragraph{Reasoning Unit.}
This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as
determining the location of the correct object for reasoning.
To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
First, we take the visual attention vector $\vec{va}_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
and compute a simple aggregate\footnote{%
	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
$vs_t = \sum_{i=1}^L [\vec{va}_t(i)]^2$. It can be shown that the more localized the attention
vector is, the higher is the aggregate value.
We perform a similar computation on the read head $\rhead_t$ over memory locations.
We feed these two values along with the temporal class weights $\bm{\tau}_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
in $[0,1]$ modulated for the current reasoning step:
(a) $\imatch_t$, which determines whether there is a valid visual object;
(b) $\mmatch_t$, which determines whether there is a valid memory object. 
(c) $\doreplace_t$, which determines whether the memory should be updated by replacing a previously stored object with a new one; and
(d) $\doadd_t$, which determines whether a new object should be added to memory.
We stress that the network has to learn via training how to correctly implement these behaviors.
